wfmash: whole-chromosome pairwise alignment using the hierarchical wavefront algorithm

### 2021-12-04 manuscript/main.tex
add affiliation; start simulations workflow for Octopus

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Milan, Italy \\
$^{\text{\sf 2}}$???, ???, Pisa, Italy \\
$^{\text{\sf 3}}$Department of Computer Sciences, Barcelona Supercomputing Center, Barcelona 08034, Spain \\
$^{\text{\sf 4}}$Departament d’Arquitectura de Computadors i Sistemes Operatius, Universitat Autònoma de Barcelona, Barcelona 08193, Spain \\
$^{\text{\sf 5}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

>>>>

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Milan, Italy \\
$^{\text{\sf 2}}$Department of Computer Sciences, University of Pisa, Pisa, Italy \\
$^{\text{\sf 3}}$Department of Computer Sciences, Barcelona Supercomputing Center, Barcelona 08034, Spain \\
$^{\text{\sf 4}}$Departament d’Arquitectura de Computadors i Sistemes Operatius, Universitat Autònoma de Barcelona, Barcelona 08193, Spain \\
$^{\text{\sf 5}}$University of Tennessee Health Science Center, Memphis, TN, USA
}
